\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-30 Proposal.tex
Final Draft 1

\begin{figure}[H]
        \centering
                \fbox{\includegraphics[width=0.8\textwidth]{assets/model}}
                \caption{From Data to Knowledge}
                \label{fig:dataknow}
\end{figure}

@@

In this example in the first part of the sentence, information pertaining to my sister and to a circus are introduced, i.e. \textit{discourse-new}. In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced.\\

>>>>

\begin{figure}[H]
        \centering
                \fbox{\includegraphics[width=0.8\textwidth]{assets/model2}}
                \caption{From Data to Knowledge}
                \label{fig:dataknow}
\end{figure}

@@

In this example in the first part of the sentence, information pertaining to my sister and to a circus are introduced, i.e. \textit{discourse-new}. In the second part, the underlined parts are considered \textit{discourse-old} since they have already been introduced. These terms are coined to refer to the accessibility of the information to participants of the discourse \cite{Newness:npentrel14}. The accessibility depends on the relative \textit{newness}, i.e. recency of mention, of this information.\\
